The benefits of an extended feature space in a machine learning bot for the game Schnapsen

### 2018-02-01 Text/paper.tex
added standard deviations (of all the means) to the findings

\begin{center}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotRand.png}
\captionof{figure}{Part of games won against Rand}
\end{minipage}
\hfill
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotBully.png}
\captionof{figure}{Part of games won against Bully}
\end{minipage}
      \\ %extra line for space
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotRdeep.png}
\captionof{figure}{Part of games won against Rdeep (notice the Y-axis)}
\end{minipage}
\end{center}

@@

\subsection*{Against Rand}

\subsection*{Against Bully}

\subsection*{Against Rdeep}
First of all, the learning bots performed worse than rdeep.The worst performer was, surprisingly, the stock ml bot. The performance of each bot

>>>>

\begin{center}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotRand.png}
\captionof{figure}{Part of games won against Rand}
\end{minipage}
\hfill
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotBully.png}
\captionof{figure}{Part of games won against Bully}
\end{minipage}
      \\ %extra line for space
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotRdeep.png}
\captionof{figure}{Part of games won against Rdeep (please notice the Y-axis)}
\end{minipage}
\end{center}

@@

\subsection*{Against Rand}
The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rand is 0.06524314

\subsection*{Against Bully}
The \textit{standard deviation} of the mean of the 9 tournaments for each bot against bully is 0.0432435

\subsection*{Against Rdeep}
The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rdeep is 0.02804758.
First of all, the learning bots performed worse than rdeep. The worst performer was, surprisingly, the stock ml bot. However, the results of the bots are relatively close, except for the ml\_minimal bot.
